---
title: "Problem Set 1"
author: "Jaime Song"
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}


library(knitr)

# As long as you are working in a Rstudio Project file, you shouldn't need to 'hard code' directories like this 
# change to your own working directory
#knitr::opts_knit$set(root.dir = 'C:/Users/doosti/Desktop/MGSC_310')

# set seed to your own favorite number
set.seed(310)
options(width=70)
# if you want to prevent scientific format for numbers use this:
options(scipen=99)

# general rchunk code options
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=FALSE, size = "vsmall")
opts_chunk$set(message = FALSE,
               warning = FALSE,
               cache = TRUE,
               autodep = TRUE,
               cache.comments = FALSE,
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')

```

```{r setup_2}

# load all your libraries here
library('tidyverse')
library('ggplot2')
library(ISLR)

# note, do not run install.packages() inside a code chunk. install them in the console outside of a code chunk. 

```


## Question 1

1a) Response to part a. 

```{r}
getwd()

```


1b) Response to part b. 

```{r}
movies <- read.csv("datasets/IMDB_movies.csv")

```

1c) Response to part c.

```{r}
dim(movies)

```

1d) Response to part d. 

```{r}
names(movies)

```
1e) Response to part e. 

```{r}
movies %>% 
  glimpse()
movies %>% 
  select_if(is.character) %>% 
  glimpse()

```

1f) Response to part f.

```{r}
movies %>% slice(1:5)

```
1g) Response to part g.

```{r}
movies %>% 
  arrange(-gross) %>% 
  slice(1:10) 

movies %>% 
  select(director_name) %>% 
  slice(1)
```
1h) Response to part h
```{r}
movies_sub <- movies %>% select(-facenumber_in_poster)

dim(movies)
dim(movies_sub)
```

1i) Response to part i
```{r}
movies %>% 
  filter(content_rating == "PG-13") %>% 
  count()

# From what we learned in class
movies %>% 
  filter(content_rating == "PG-13") %>% 
  summarize(mean_gross = mean(gross, na.rm = TRUE))

# Another method I found online
movies %>% 
  filter(content_rating == "PG-13") %>% 
  # pull: extracts column needed
  pull(gross) %>%
  mean(na.rm = TRUE)
```

## Question 2

2a) Response to part a. 


```{r}
data(movies)
ggplot(movies, aes(x = imdb_score, y = gross)) +
  geom_point()


```


2b) Response to part b. 


```{r}
ggplot(movies, aes(x = imdb_score, y = gross)) +
  geom_point(alpha = 0.1) 

```

2c) Response to part c. 


```{r}
movies <- movies %>% 
  mutate(gross_M = gross/1000000)
ggplot(movies, aes(x = imdb_score, y = gross_M)) +
  geom_point(alpha = 0.1)

```

2d) Response to part d. 


```{r}
ggplot(movies, aes(x = imdb_score, y = gross_M)) +
  geom_point(alpha = 0.1) +
  geom_smooth()

```

2e) Response to part e. 


```{r}
movies %>% 
  filter(director_name == "James Cameron") %>% 
  ggplot(aes(x = imdb_score, y = gross_M)) +
  geom_text(aes(label = movie_title), color = "blue")

```

2f) Response to part f. 


```{r}
movies %>% 
  filter(director_name == "James Cameron") %>% 
  ggplot(aes(x = imdb_score, y = gross_M)) +
  geom_text(aes(label = movie_title), color = "blue") +
  xlim(6, 10) + 
  ylim(0, 800)

```

2g) Response to part g. 


```{r}
movies %>% 
  filter(director_name == "James Cameron") %>% 
  ggplot(aes(x = imdb_score, y = gross_M)) +
  geom_text(aes(label = movie_title), color = "blue") +
  xlim(5, 15) + ylim(0, 800) +
  xlab("IMDB Score") + ylab("Gross Value (In millions of dollars)")

```


## Question 3

2d) Is there a relationship between movie gross and IMDB Score?

Yes, the higher the IMDB score, the higher the gross value.



