---
title: "Problem Set 2"
author: "Jaime Song"
subtitle: MGSC 310 
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}


library(knitr)

# As long as you are working in a Rstudio Project file, you shouldn't need to 'hard code' directories like this 
# change to your own working directory
#knitr::opts_knit$set(root.dir = 'C:/Users/doosti/Desktop/MGSC_310')

# set seed to your own favorite number
set.seed(310)
options(width=70)
# if you want to prevent scientific format for numbers use this:
options(scipen=99)

# general rchunk code options
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=FALSE, size = "vsmall")
opts_chunk$set(message = FALSE,
               warning = FALSE,
               cache = TRUE,
               autodep = TRUE,
               cache.comments = FALSE,
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')

```

```{r setup_2, include=FALSE}

# load all your libraries here
library(tidyverse)
library(ISLR)
library(rsample)
library(caret)
library(lindia)
# note, do not run install.packages() inside a code chunk. install them in the console outside of a code chunk. 

```


## Question 1: Predicting Movie Revenue

Part 1: Data Splitting

```{r}
data(movies)
movies <- read_csv("datasets/IMDB_movies.csv")
movies %>% glimpse()
movies_clean <- 
  movies %>% 
  mutate(budgetM = budget/1000000,
         grossM = gross/1000000,
         profitM = grossM - budgetM,
         ROI = profitM/budgetM,
         genre_main = as.factor(unlist(map(strsplit(as.character(movies$genres),"\\|"),1))) %>% fct_lump(12),
         rating_simple = fct_lump(content_rating, n = 6)
         ) %>%
  filter(budget < 400000000, 
         content_rating != "", 
         content_rating != "Not Rated",
         language == "English") %>% 
  mutate(rating_simple = rating_simple %>% fct_drop()) %>% 
  rename(director = director_name, 
         title = movie_title,
         year = title_year) %>% 
  select(-c(actor_1_name, actor_2_name,actor_1_facebook_likes, actor_2_facebook_likes, 
         budget, gross, aspect_ratio, num_voted_users,num_user_for_reviews)) %>% 
  relocate(title, year, country, director, budgetM, grossM, profitM, ROI, imdb_score, genre_main, rating_simple, language, duration)

set.seed(310)
movies_split <- initial_split(movies_clean, prop = 0.80)
movies_train <- training(movies_split)
movies_test <- testing(movies_split)

```


Part 2: Linear Regression

```{r}
movies_train$rating_simple <- relevel(movies_train$rating_simple, ref = "R")
model1 <- lm(grossM ~ imdb_score + budgetM + rating_simple, movies_train)
summary(model1)

# The Multiple R-squared is 0.4878, meaning about 48.78% of the variance in grossM is explained by the predictors (imdb_score, budgetM, and rating_simple)

# The Adjusted R-squared is 0.4866, which is slighly lower but still close, indicating that the adding predictors has improved the model without overfitting
```

Part 3: Interpretation

BudgetM Coefficient Interpretation:
The coefficient for budgetM is 0.97327 meaning that for each additional million dollars spent on a movie, the expected gross revenue increases by $0.97 million on average. Spending more does not necessarily mean greater net profit. A higher budget correlates with higher revenue but it does not account for costs. For example, if a movie spends an extra $10 million, it is expected to earn about $9.73 million more in revenue, which is a negative return on investment. Therefore, higher spending does not always guarantee higher net profit.


Rating Interpretation:
The coefficient for rating_simpleG is 33.75 meaning that on average G-rated movies earn $33.75 million more in revenue than R-rated movies, assuming all other factors are the same. This suggests that G-rated movies tend to have a broader audience appeal, leading to higher box office revenues compared to R-rated movies, which have a restricted audience. 

P-value Explanation:
The p-value for imdb_score is < 0.0000000000000002 which is extremely small. A p-value measures the probability of observing a relationship this strong between imdb_score and revenue purely by chance, assuming there is actually no true relationship. A very small p-value (< 0.05) means we have strong evidence to reject the null hypothesis. Since the p-value is so small, we can conclude with high confidence that imdb_score has a statistically significant positive relationship with revenue. Therefore, higher IMDb scores are strongly associated with higher box office earnings. 


Part 4: Prediction and Evaluation


```{r}
grossM_train <- predict(model1, newdata = movies_train)
RMSE(grossM_train, movies_train$grossM)

grossM_test <- predict(model1, newdata = movies_test)
RMSE(grossM_test, movies_test$grossM)

results_test <- data.frame(
  preds = grossM_test,
  actual = movies_test$grossM
)

# create a scatter plot for actual vs predicted
ggplot(results_test, aes(x = actual, y = preds)) +
  geom_point() +
  xlab("Actual GrossM") +
  ylab("Predicted GrossM")
```


Part 5: Reflection

One specific limitation of the model is that it does not account for marketing and distribution factors, which can have a major impact on a movie's revenue. A movie with a moderate budget but strong marketing might outperform a high-budget film with poor promotion. One way to improve this model could be to integatre the variable movie_facebook_likes to understand how audience anticipation correlates with box office performance. 